Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-20 manuscript.tex
Added citations for ionization history figure

\begin{figure}[h!]
\centering
    \includegraphics[width=0.51\textwidth,clip]{plots/ionHist.pdf}
  \caption{Combining direct constraints on $x_\text{HI}$, the hydrogen neutral fraction, as a function of redshift (black points) with \emph{Planck} priors yields
an inferred $95\%$ confidence region (gray).  HERA constraints with (dark red) and without (pale red) 
a conservative $25\%$ modeling error in the $21\,\textrm{cm}$ power spectrum can dramatically narrow this confidence region.}
	\label{fig:IonHist}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=0.51\textwidth,clip]{plots/ionHist.pdf}
  \caption{Combining direct constraints on $x_\text{HI}$, the hydrogen neutral fraction, as a function of redshift (black points) with \emph{Planck} priors \citep{planck_et_al2015} yields
an inferred $95\%$ confidence region (gray; Greig \& Mesinger, in prep.).  HERA constraints with (dark red) and without (pale red) 
a conservative $25\%$ modeling error in the $21\,\textrm{cm}$ power spectrum can dramatically narrow this confidence region \citep{liu_parsons2015}. Included for reference are constraints from the fraction of Lyman-alpha emitting galaxies \citep{pentericci_et_al2014,schenker_et_al2014}, quasar near-zone studies \citep{mortlock_et_al2011,bolton_et_al2011,schroeder_et_al2013}, Lyman-alpha galaxy clustering \citep{mcquinn_et_al2007_lya_clustering,ouchi_et_al2010}, and counts of dark Lyman-alpha pixels \citep{mcgreer_et_al2015}.}
	\label{fig:IonHist}
\end{figure}
